Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-03 paper/main.tex
paper table

@@

\newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
%\begin{table*}[tb]
%  \caption{Mean fitness (and standard deviation) of the best solution found. % at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. 
%  Mean runtime is shown in hours. 
%  %CEGO runs were stopped after 144 hours. This was the case for all LOP instances.
%  \label{tab:results}}
%  \resizebox{\textwidth}{!}{%
%\begin{tabular}{r@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}
% \toprule
%            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
%            \bf Problem & \bf     Instance & \mcolc{2}{CEGO} & \mcolc{2}{UMM}   &                         &            & \bf & \bf CEGO       & \bf UMM                       \\\midrule

\begin{table*}[tb] % resumns
\begin{tabular}{l@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}%llrlrllrrr}
\toprule
%Problem &    Instance &  CEGO\_Fitness\_mean & CEGO\_Fitness\_std &  UMM\_Fitness\_mean & UMM\_Fitness\_std &    Confidence interval &  CEGO F. evaluations &  CEGO Runtime &  UMM Runtime \\
            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
            \bf Problem & \bf     Instance & \mcolc{2}{CEGO} & \mcolc{2}{UMM}   &                         &            & \bf & \bf CEGO       & \bf UMM                       \\\midrule
\midrule
    LOP &    N-p40-01 &            10496.6 &          (116.8) &           12369.1 &         (389.9) &     [-2157.1, -1587.9] &                400.0 &          19.9 &          0.3 \\
    LOP &    N-p40-02 &            11714.7 &           (84.7) &           13160.5 &         (454.8) &     [-1773.5, -1118.1] &                400.0 &          20.1 &          0.3 \\
    LOP &  N-t59b11xx &           102408.0 &         (3800.2) &          114075.5 &        (5389.2) &    [-16084.2, -7250.8] &                400.0 &          21.1 &          0.4 \\
    LOP &  N-t59d11xx &            12692.2 &         (1097.9) &           16662.9 &        (2155.3) &     [-5618.5, -2322.9] &                400.0 &          21.2 &          0.4 \\
    LOP &    N-p50-02 &            19090.5 &          (285.4) &           21746.6 &         (645.4) &     [-3140.6, -2171.6] &                400.0 &          22.9 &          0.5 \\
    LOP &    N-p50-01 &            18197.7 &          (225.6) &           21161.8 &         (657.4) &     [-3447.4, -2480.8] &                400.0 &          23.2 &          0.5 \\
    LOP &  N-sgb75.01 &          1893533.2 &        (28594.6) &         1992059.9 &       (40235.7) &  [-131577.1, -65476.3] &                400.0 &          33.2 &          1.0 \\
    LOP &  N-sgb75.02 &          1895801.8 &        (82847.9) &         1967132.3 &       (49228.1) &   [-136421.2, -6239.8] &                400.0 &          33.3 &          1.1 \\
   PFSP &       rec05 &             1276.2 &           (15.1) &            1276.3 &           (8.4) &          [-11.8, 11.6] &                400.0 &          18.3 &          0.1 \\
   PFSP &       rec13 &             1992.9 &           (27.6) &            2057.8 &          (22.8) &         [-88.8, -41.0] &                400.0 &          18.5 &          0.1 \\
   PFSP &       rec19 &             2264.5 &           (45.0) &            2304.8 &          (37.7) &          [-79.4, -1.2] &                400.0 &          18.2 &          0.2 \\
   PFSP &       rec31 &             3415.5 &           (62.1) &            3419.3 &          (37.0) &          [-52.6, 45.0] &                400.0 &          23.1 &          0.5 \\
\bottomrule
\end{tabular} 
\end{table*}

>>>>

% \usepackage{multirow}
\usepackage{xcolor}

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}[]
\begin{tabular}{rrrrrrrrr}
\multicolumn{1}{c}{\textbf{}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{4}{c}{\textbf{Mean fitness (sd)}}                       & \multicolumn{1}{c}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}95\% CI of the \\ mean difference\end{tabular}}}} & \multicolumn{2}{c}{\textbf{Runtime}} \\ \cline{3-6} \cline{8-9} 
\textbf{Problem}              & \textbf{Instance}             & \multicolumn{2}{r}{\textbf{CEGO}} & \multicolumn{2}{r}{\textbf{UMM}} & \multicolumn{1}{c}{}                                                                                                    & \textbf{CEGO}     & \textbf{UMM}     \\ \hline
LOP                           & N-p40-01                      & 10496.6          & (116.8)        & 12369.1         & (389.9)        & {[}-2157.1, -1587.9{]}                                                                                                  & 19.9              & 0.3              \\
LOP                           & N-p40-02                      & 11714.7          & (84.7)         & 13160.5         & (454.8)        & {[}-1773.5, -1118.1{]}                                                                                                  & 20.1              & 0.3              \\
LOP                           & N-t59b11xx                    & 102408.0         & (3800.2)       & 114075.5        & (5389.2)       & {[}-16084.2, -7250.8{]}                                                                                                 & 21.1              & 0.4              \\
LOP                           & N-t59d11xx                    & 12692.2          & (1097.9)       & 16662.9         & (2155.3)       & {[}-5618.5, -2322.9{]}                                                                                                  & 21.2              & 0.4              \\
LOP                           & N-p50-02                      & 19090.5          & (285.4)        & 21746.6         & (645.4)        & {[}-3140.6, -2171.6{]}                                                                                                  & 22.9              & 0.5              \\
LOP                           & N-p50-01                      & 18197.7          & (225.6)        & 21161.8         & (657.4)        & {[}-3447.4, -2480.8{]}                                                                                                  & 23.2              & 0.5              \\
LOP                           & N-sgb75.01                    & 1893533.2        & (28594.6)      & 1992059.9       & (40235.7)      & {[}-131577.1, -65476.3{]}                                                                                               & 33.2              & 1.0              \\
LOP                           & N-sgb75.02                    & 1895801.8        & (82847.9)      & 1967132.3       & (49228.1)      & {[}-136421.2, -6239.8{]}                                                                                                & 33.3              & 1.1              \\
PFSP                          & rec05                         & 1276.2           & (15.1)         & 1276.3          & (8.4)          & {[}-11.8, 11.6{]}                                                                                                       & 18.3              & 0.1              \\
PFSP                          & rec13                         & 1992.9           & (27.6)         & 2057.8          & (22.8)         & {[}-88.8, -41.0{]}                                                                                                      & 18.5              & 0.1              \\
PFSP                          & rec19                         & 2264.5           & (45.0)         & 2304.8          & (37.7)         & {[}-79.4, -1.2{]}                                                                                                       & 18.2              & 0.2              \\
PFSP                          & rec31                         & 3415.5           & (62.1)         & 3419.3          & (37.0)         & {[}-52.6, 45.0{]}                                                                                                       & 23.1              & 0.5             
\end{tabular}
\end{table*}
